---
title: "Appendix"
author: "Iker Caballero Bragagnini"
date: "2023-04-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Package Installing

```{r,results='hide',fig.show='hide'}
library(tseries)
library(fBasics)
library(car)
library(tseries)
library(urca)
library(forecast)
library(rugarch)
library(quantmod)
library(ggplot2)
library(fTrading)
library(rmgarch)
```

# Exploratory Analysis

### Data Import

```{r,results='hide',fig.show='hide'}
getSymbols("^N225",from="2000-01-01", to="2022-12-30")
dim(N225)
head(N225)
tail(N225)
nik=N225[,6]
```

### Graphs

```{r,results='hide',fig.show='hide'}
plot(nik,main="Nikkei 225")
nik<-na.locf(nik, fromLast = TRUE)
length(nik)
plot(nik,main="Nikkei 225")
```

```{r,results='hide',fig.show='hide'}
rendnik=diff(log(nik))
rendnik<-rendnik[-1]

par(mfrow=c(2,1))
plot(nik,main="Nikkei 225")
plot(rendnik, main="Returns Nikkei 225")
```

### Stationarity

###### ACF & PACF

```{r,results='hide',fig.show='hide'}
par(mfrow=c(1,2)) 
acf(nik,ylim=c(-1,1),main="Nikkei 225")
pacf(nik,ylim=c(-1,1),main="Nikkei 225")

par(mfrow=c(1,2)) 
acf(rendnik,ylim=c(-1,1),main="Returns Nikkei 225")
pacf(rendnik,ylim=c(-1,1),main="Returns Nikkei 225")
```

###### Independence of lags

```{r,results='hide',fig.show='hide'}
Box.test(nik, lag = 1, type = c("Ljung-Box"))
Box.test(nik, lag = 5, type = c("Ljung-Box"))
Box.test(nik, lag = 10, type = c("Ljung-Box"))
Box.test(nik, lag = 15, type = c("Ljung-Box"))
Box.test(nik, lag = 20, type = c("Ljung-Box"))

Box.test(rendnik, lag = 1, type = c("Ljung-Box"))
Box.test(rendnik, lag = 5, type = c("Ljung-Box"))
Box.test(rendnik, lag = 10, type = c("Ljung-Box"))
Box.test(rendnik, lag = 15, type = c("Ljung-Box"))
Box.test(rendnik, lag = 20, type = c("Ljung-Box"))
```

###### Unit root tests for prices

```{r,results='hide',fig.show='hide'}
# Tests
nik.df.b<-ur.df(nik, lags=20, selectlags = c("BIC"))
nik.df.db<-ur.df(nik, type = c("drift"), lags=20, selectlags = c("BIC"))
nik.df.tb<-ur.df(nik, type = c("trend"), lags=20, selectlags = c("BIC"))
nik.pp.c<-ur.pp(nik, type = c("Z-tau"), model = c("constant"), use.lag = 20)
nik.pp.t<-ur.pp(nik, type = c("Z-tau"), model = c("trend"), use.lag = 20)
nik.kpss.c<-ur.kpss(nik, type = c("mu"), use.lag = 20)
nik.kpss.t<-ur.kpss(nik, type = c("tau"), use.lag = 20)

# Summary
summary(nik.df.b)
summary(nik.df.db)
summary(nik.df.tb)
summary(nik.pp.c)
summary(nik.pp.t)
summary(nik.kpss.c)
summary(nik.kpss.t)

# Plot
plot(nik.df.b)
plot(nik.df.db)
plot(nik.df.tb)
plot(nik.pp.c)
plot(nik.pp.t)
plot(nik.kpss.t)
```

###### Unit root tests for returns

```{r,results='hide',fig.show='hide'}
# Tests
rendnik.df.b<-ur.df(rendnik, lags=20, selectlags = c("BIC"))
rendnik.df.db<-ur.df(rendnik, type = c("drift"), lags=20, selectlags = c("BIC"))
rendnik.df.tb<-ur.df(rendnik, type = c("trend"), lags=20, selectlags = c("BIC"))
rendnik.pp.c<-ur.pp(rendnik, type = c("Z-tau"), model = c("constant"), use.lag = 20)
rendnik.pp.t<-ur.pp(rendnik, type = c("Z-tau"), model = c("trend"), use.lag = 20)
rendnik.kpss.c<-ur.kpss(rendnik, type = c("mu"), use.lag = 20)
rendnik.kpss.t<-ur.kpss(rendnik, type = c("tau"), use.lag = 20)

# Summary
summary(rendnik.df.b)
summary(rendnik.df.db)
summary(rendnik.df.tb)
summary(rendnik.pp.c)
summary(rendnik.pp.t)
summary(rendnik.kpss.c)
summary(rendnik.kpss.t)
```

### Basic Statistics

```{r,results='hide',fig.show='hide'}
normalTest(rendnik,method="jb")
normalTest(nik,method="jb")
basicStats(rendnik)
round(basicStats(nik),3)
```

```{r,results='hide',fig.show='hide'}
hist(rendnik,breaks=20,freq=F, main = "Nikkei225 Log-returns")
curve(dnorm(x, mean=mean(rendnik), sd=sd(rendnik)), col=2, add=T)
```

# ARMA Model Identification, Estimation & Diagnosis

### Model Identification

```{r,results='hide',fig.show='hide'}
par(mfrow=c(1,2),font=2,font.lab=4,font.axis=2,las=1)
acf(rendnik,ylim=c(-1,1),main="Returns Nikkei 225")
pacf(rendnik,ylim=c(-1,1),main="Returns Nikkei 225")
```

### Model Estimation

```{r,results='hide',fig.show='hide'}
# White noise
model_w = Arima(rendnik, order = c(0,0,0),include.mean = TRUE)
model_w

# AR(1)
model_ar1 = Arima(rendnik, order = c(1,0,0),include.mean = TRUE)
model_ar1

# MA(1)
model_ma1 = Arima(rendnik, order = c(0,0,1),include.mean = TRUE)
model_ma1
```

### Diagnosis

```{r,results='hide',fig.show='hide'}
autoplot(model_ar1)
tsdiag(model_ar1)
par(mfrow=c(1,2),font=2,font.lab=4,font.axis=2,las=1)
acf(model_ar1$residuals,ylim=c(-1,1),main="residuosar2")
pacf(model_ar1$residuals,ylim=c(-1,1),main="residuosar2")

qqnorm(model_ar1$residuals)
qqline(model_ar1$residuals, datax = FALSE)
normalTest(model_ar1$residuals,method="jb")
```

# GARCH Identification, Estimation & Diagnosis

### Model Identification

```{r,results='hide',fig.show='hide'}
residuos=model_ar1$residuals
residuos2=residuos^2

par(mfrow=c(1,2),font=2,font.lab=4,font.axis=2,las=1)
acf(residuos2,ylim=c(-1,1)) 
pacf(residuos2,ylim=c(-1,1))

Box.test(residuos2,lag=1,type='Ljung')
Box.test(residuos2,lag=5,type='Ljung')
Box.test(residuos2,lag=15,type='Ljung')
Box.test(residuos2,lag=20,type='Ljung')
```

### Model Estimation GARCH

```{r,results='hide',fig.show='hide'}
# Model_ar1
spec_ar1=ugarchspec(variance.model = list(model = "sGARCH", 
garchOrder = c(1,1)), mean.model=list(armaOrder=c(1,0)), 
distribution.model = "std")
m_ar1 = ugarchfit(spec=spec_ar1,data=rendnik)
m_ar1

v_GARCH_ar1 = sigma(m_ar1)
v_anualizada_GARCH_ar1=(250)^0.5*v_GARCH_ar1
```

### Model Estimation EGARCH

```{r,results='hide',fig.show='hide'}
spec2=ugarchspec(variance.model=list(model="eGARCH", garchOrder = c(1,1)),mean.model=list(armaOrder=c(1,0)), distribution.model = "std")
m2_ar1=ugarchfit(spec=spec2,data=rendnik)
m2_ar1

v_GARCH_e = sigma(m2_ar1)
v_anualizada_GARCH_e=(250)^0.5*v_GARCH_e
```

### Model Estimation GJR-GARCH

```{r,results='hide',fig.show='hide'}
spec3=ugarchspec(variance.model=list(model="gjrGARCH", garchOrder = c(1,1)), mean.model=list(armaOrder=c(1,0)), distribution.model = "std")
m3_ar1=ugarchfit(spec=spec3,data=rendnik)
m3_ar1

v_GJR_GARCH = sigma(m3_ar1)
v_anualizada_GJR_GARCH=(250)^0.5*v_GJR_GARCH 

vol.obs <- (250)^0.5*abs(rendnik)
```

### Graph

```{r,results='hide',fig.show='hide'}
plot(vol.obs,col="black", main="Estimated Volatility",
     cex.main=0.5,
     ylim=c(0,2.3))
lines(v_anualizada_GARCH_ar1,ylab="1 = 100%",col="blue")
lines(v_anualizada_GARCH_e,ylab="1 = 100%",col="darkgreen")
lines(v_anualizada_GJR_GARCH,ylab="1 = 100%",col="darkred")
```

# News Impact

```{r,results='hide',fig.show='hide'}
ni1=newsimpact(z = NULL, m_ar1)
ni2=newsimpact(z = NULL, m2_ar1)
ni3=newsimpact(z = NULL, m3_ar1)
plot(ni1$zx, ni1$zy, ylab=ni1$yexpr, xlab=ni1$xexpr, type="l", col="blue", 
     ylim=c(0.00015,0.0026),main = "News Impact Curves for the Models")
lines(ni2$zx, ni2$zy, ylab=ni2$yexpr, xlab=ni2$xexpr, type="l", 
      col="darkgreen")
lines(ni3$zx, ni3$zy, ylab=ni3$yexpr, xlab=ni3$xexpr, type="l", 
      col="darkred")
```

# Prediction

### Static

```{r,results='hide',fig.show='hide'}
mpred_ar1=ugarchfit(spec=spec_ar1,data=rendnik,out.sample = 90)
forc = ugarchforecast(mpred_ar1, n.ahead=90, n.roll= 0)
show(forc)
mpred_ar1@model$modeldata$T

round(fpm(forc),6)

uncvariance(m_ar1)^0.5

mpred_e=ugarchfit(spec=spec2,data=rendnik,out.sample = 90)
forc2 = ugarchforecast(mpred_e, n.ahead=90, n.roll= 0)
show(forc2)
mpred_e@model$modeldata$T

round(fpm(forc2),6)

uncvariance(m2_ar1)^0.5

mpred_gjr=ugarchfit(spec=spec3,data=rendnik,out.sample = 90)
forc3 = ugarchforecast(mpred_gjr, n.ahead=90, n.roll= 0)
show(forc3)
mpred_gjr@model$modeldata$T

round(fpm(forc3),6)
uncvariance(m3_ar1)^0.5
```

### Dynamic

```{r,results='hide',fig.show='hide'}
forc_1 = ugarchforecast(mpred_ar1, n.ahead=1, n.roll= 90)
show(forc_1)
mpred_ar1@model$modeldata$T

round(fpm(forc_1),5)
uncvariance(m_ar1)^0.5

forc2_1 = ugarchforecast(mpred_e, n.ahead=1, n.roll= 90) 
mpred_e@model$modeldata$T

round(fpm(forc2_1),5)
uncvariance(m2_ar1)^0.5

mpred_gjr_1=ugarchfit(spec=spec3,data=rendnik,out.sample = 90)
forc3_1 = ugarchforecast(mpred_gjr, n.ahead=1, n.roll= 90)
show(forc3_1)
mpred_gjr@model$modeldata$T

round(fpm(forc3_1),5)
uncvariance(m3_ar1)^0.5
```

# Historical & EMWA volatility

### Historical Volatility

```{r,results='hide',fig.show='hide'}
Fechas<-as.Date(rownames(zoo(nik)))
Fechas<-Fechas[-1] #eliminamos la primera observación de Fechas, la hemos perdido al calcular los rendimientos
Tf=length(Fechas)

resid.mod<- m_ar1@fit$residuals 

n_vol=5 # periodos de media móvil
vol.hist20 <- sqrt(SMA(resid.mod^2, n=n_vol) * 252)
Fechas2<-Fechas[(n_vol+1):(Tf+1)]#hemos perdido las primeras 20 observaciones para calcular la primera varianza. Añadimos una observación m?s dado que con las 20 últimas observaciones calculamos la volatilidad 1 paso hacia adelante.

n_vol=21
vol.hist80 <- sqrt(SMA(resid.mod^2, n=n_vol) * 252)
Fechas3<-Fechas[(n_vol+1):(Tf+1)]

n_vol=63
vol.hist160 <- sqrt(SMA(resid.mod^2, n=n_vol) * 252)
Fechas4<-Fechas[(n_vol+1):(Tf+1)]

n_vol=126
vol.hist240 <- sqrt(SMA(resid.mod^2, n=n_vol) * 252)
Fechas5<-Fechas[(n_vol+1):(Tf+1)]

par(mfrow=c(2,2), cex=0.6, mar=c(2,2,3,1))
plot(Fechas2, vol.hist20, type="l", ylab='variance', main='1 week moving average')
lines(Fechas, v_anualizada_GJR_GARCH, type="l", ylab='variance',col="darkred",
      lwd=0.5)
plot(Fechas3, vol.hist80, type="l", ylab='variance', main='1 month moving average')
lines(Fechas, v_anualizada_GJR_GARCH, type="l", ylab='variance',col="darkred",
      lwd=0.5)
plot(Fechas4, vol.hist160, type="l", ylab='variance', main='3 month moving average')
lines(Fechas, v_anualizada_GJR_GARCH, type="l", ylab='variance',col="darkred",
      lwd=0.5)
plot(Fechas5, vol.hist240, type="l", ylab='variance', main='6 month moving average')
lines(Fechas, v_anualizada_GJR_GARCH, type="l", ylab='variance',col="darkred",
      lwd=0.5)
```

### Exponential Weighted Moving Average

```{r,results='hide',fig.show='hide'}
vol.ewma0.95 <- sqrt(EWMA(resid.mod^2, lambda = 0.05)*252)# note: in EWMA lambda is actually 1-lambda
vol.ewma0.75 <-  sqrt(EWMA(resid.mod^2, lambda = 0.25)*252) # note: in EWMA lambda is actually 1-lambda
vol.ewma0.5 <-  sqrt(EWMA(resid.mod^2, lambda = 0.5)*252) # note: in EWMA lambda is actually 1-lambda
vol.ewma0.25 <-  sqrt(EWMA(resid.mod^2, lambda = 0.75)*252) # note: in EWMA lambda is actually 1-lambda

par(mfrow=c(2,2), cex=0.6, mar=c(2,2,3,1))
plot(Fechas, vol.ewma0.95, type="l", ylab='variance', main='EWMA 0.95')
lines(Fechas, v_anualizada_GJR_GARCH, type="l", ylab='variance',col="darkred",
      lwd=0.5)
plot(Fechas, vol.ewma0.75, type="l", ylab='variance', main='EWMA 0.75')
lines(Fechas, v_anualizada_GJR_GARCH, type="l", ylab='variance',col="darkred",
      lwd=0.5)
plot(Fechas, vol.ewma0.5, type="l", ylab='variance', main='EWMA 0.5')
lines(Fechas, v_anualizada_GJR_GARCH, type="l", ylab='variance',col="darkred",
      lwd=0.5)
plot(Fechas, vol.ewma0.25, type="l", ylab='variance', main='EWMA 0.25')
lines(Fechas, v_anualizada_GJR_GARCH, type="l", ylab='variance',col="darkred",
      lwd=0.5)

```

# VAR estimation

```{r,results='hide',fig.show='hide'}
spec1=ugarchspec(variance.model=list(model="gjrGARCH", garchOrder = c(1,1)), mean.model=list(armaOrder=c(1,0)), distribution.model = "std")
var.t=ugarchroll(spec1, data = rendnik, n.ahead = 1, forecast.length = 252, 
refit.every = 21, calculate.VaR = TRUE, VaR.alpha = 0.05,refit.window = "rolling")

spec2=ugarchspec(variance.model=list(model="sGARCH", garchOrder = c(1,1)), mean.model=list(armaOrder=c(1,0)), distribution.model = "std")
var.t2=ugarchroll(spec2, data = rendnik, n.ahead = 1, forecast.length = 252, 
refit.every = 21, calculate.VaR = TRUE, VaR.alpha = 0.05,refit.window = "rolling")

spec3=ugarchspec(variance.model=list(model="eGARCH", garchOrder = c(1,1)), mean.model=list(armaOrder=c(1,0)), distribution.model = "std")
var.t3=ugarchroll(spec3, data = rendnik, n.ahead = 1, forecast.length = 252,
refit.every = 21, calculate.VaR = TRUE, VaR.alpha = 0.05,refit.window = "rolling")


plot(Fechas[(length(Fechas)-252+1):length(Fechas)],
     var.t@forecast$VaR$`alpha(5%)`,type="l",ylab="VAR 95%",xlab="",col="darkred")
lines(Fechas[(length(Fechas)-252+1):length(Fechas)],
     var.t2@forecast$VaR$`alpha(5%)`,type="l",ylab="VAR 95%",xlab="",col="blue")
lines(Fechas[(length(Fechas)-252+1):length(Fechas)],
     var.t3@forecast$VaR$`alpha(5%)`,type="l",ylab="VAR 95%",xlab="",col="darkgreen")


spec199=ugarchspec(variance.model=list(model="gjrGARCH", garchOrder = c(1,1)), mean.model=list(armaOrder=c(1,0)), distribution.model = "std")
var.t99=ugarchroll(spec1, data = rendnik, n.ahead = 1, forecast.length = 252, 
refit.every = 21, calculate.VaR = TRUE, VaR.alpha = 0.01,refit.window = "rolling")

spec299=ugarchspec(variance.model=list(model="sGARCH", garchOrder = c(1,1)), mean.model=list(armaOrder=c(1,0)), distribution.model = "std")
var.t299=ugarchroll(spec2, data = rendnik, n.ahead = 1, forecast.length = 252, 
refit.every = 21, calculate.VaR = TRUE, VaR.alpha = 0.01,refit.window = "rolling")

spec399=ugarchspec(variance.model=list(model="eGARCH", garchOrder = c(1,1)), mean.model=list(armaOrder=c(1,0)), distribution.model = "std")
var.t399=ugarchroll(spec3, data = rendnik, n.ahead = 1, forecast.length = 252, 
refit.every = 21, calculate.VaR = TRUE, VaR.alpha = 0.01,refit.window = "rolling")


plot(Fechas[(length(Fechas)-252+1):length(Fechas)],
     var.t99@forecast$VaR$`alpha(1%)`,type="l",ylab="VAR 99%",xlab="",col="darkred")
lines(Fechas[(length(Fechas)-252+1):length(Fechas)],
     var.t299@forecast$VaR$`alpha(1%)`,type="l",ylab="VAR 99%",xlab="",col="blue")
lines(Fechas[(length(Fechas)-252+1):length(Fechas)],
     var.t399@forecast$VaR$`alpha(1%)`,type="l",ylab="VAR 99%",xlab="",col="darkgreen")
```

# Multivariant GARCH Models

```{r,results='hide',fig.show='hide'}
# Mean and Volatility for FTSE100

getSymbols("^FTSE",src="yahoo",from="2000-01-01", to="2022-12-30")  

fts=FTSE[,6]
head(fts)
plot(fts)
dim(fts)
fts<-na.locf(fts, fromLast = TRUE)
rendfts <- dailyReturn(fts)

rX = cbind(rendnik, rendfts)

spec_fts = ugarchspec(mean.model = list(armaOrder = c(1,0)), variance.model = 
list(garchOrder = c(1,1), model = "sGARCH"), distribution.model = "std") 
mod_fts1=ugarchfit(spec=spec_fts,data=rendfts)
mod_fts1

spec_fts2 = ugarchspec(mean.model = list(armaOrder = c(1,0)), variance.model = 
list(garchOrder = c(1,1), model = "eGARCH"), distribution.model = "std") 
mod_fts2=ugarchfit(spec=spec_fts2,data=rendfts) # -6.5266
mod_fts2

spec_fts3 = ugarchspec(mean.model = list(armaOrder = c(1,0)), variance.model = 
list(garchOrder = c(1,1), model = "gjrGARCH"), distribution.model = "std") 
mod_fts3=ugarchfit(spec=spec_fts3,data=rendfts) # -6.5213
mod_fts3

# DCC-GARCH

mod_1 = ugarchspec(mean.model = list(armaOrder = c(1,0)), variance.model = 
list(garchOrder = c(1,1), model = "gjrGARCH"), distribution.model = "std")
mod_2 = ugarchspec(mean.model = list(armaOrder = c(1,0)), variance.model = 
list(garchOrder = c(1,1), model = "eGARCH"), distribution.model = "std") 
dcc.garch11 = dccspec(uspec = multispec(c(mod_1,mod_2)), dccOrder = c(1,1), 
distribution = "mvt")
dcc.fit = dccfit(dcc.garch11, data = na.omit(rX))
dcc.fit

# Correlation and News Impact

cor1 = rcor(dcc.fit)
dim(cor1)
cor1
cor_AM <- cor1[1,2,]
cor_AM <- as.xts(cor_AM)
plot(cor_AM,main="Correlation Between Nikkei225 and FTSE100")

write.table(cor_AM,file="correlaciones.csv")
nisurface(dcc.fit,type="cor")
```


